Survivable Set Connectivity

### 2015-05-07 draft.tex
adding files and did cost proof

For each $q$ and $v$, $v$ is $q$-marked with probability at most $\frac{4}{2^{-q}}$. In any of the $\tau'$ iterations of the RoundGKR algorithm where $v$ was $q$-marked, an edge is selected with probability $2^{q+1}y_e$.

Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e$ is included is at most 
\begin{align}
height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_e \tau' &= height(T) \tau' y_2 \sum_q 2 \\
&= O(\log^3 n) y_e 
\end{align}
This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values.

So we have shown that the probability that a given edge is included in a particular sampling of a Racke tree is $O(\log^3 n) y_e$.

\end{proof}

>>>>

For each $q$ and $v$, $v$ is $q$-marked with probability at most $\frac{4}{2^{-q}}$. In any of the $\tau'$ iterations of the RoundGKR algorithm where $v$ was $q$-marked, an edge is selected with probability $2^{q+1}y_e$. Figure~\ref{fig:roundgkronnode} shows a possible execution when there is some value of flow found when node $v$ has been $q$-marked.

Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
\begin{align}
height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
&= O(\log^3 n) y_{e'} 
\end{align}
This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values.

So we have shown that the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.

So now in order to include some edge $e$ of the graph, we must include some edge $e' \in \text{map}^{-1}(e)$. So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$, and $Y_{e'}$ be the indicator random variable which says that edge $e'$ in the tree is included in some RoundGKR execution. Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
\begin{align}
X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
\end{align}
Because if $e$ is included in the graph, it must have come from some edge in the tree. 
\begin{align}
 \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
        & = \dfrac{O(\log^4 n)\tau}{k} x_e
\end{align}
So now, bounding the optimum, we get
\begin{align}
\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
\end{align}
So when $\tau = O(\log h + k)$, we get our desired approximation.
\end{proof}

\begin{figure}
\label{fig:roundgkronnode}
\centering
\includegraphics[width=\linewidth]{RoundGKRonNode.pdf}
\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
\end{figure}
